\bf\mftitle

### 2011-03-01 doc/jInfer/xsdimport/xsdimport.tex
Fixed XSDImport according to second annotations.

None of the modules provide nor require any tokens. Complete dependency tree is depicted in Figure 9 and described in \cite[section 4]{archdoc}.

@@

Firstly, it is an extension of the \code{BasicIGG} module, registering a service provider
of a \code{Processor} class, to handle files with \emph{xsd} extension (see \cite[section 3]{basiciggdoc}). 
It defines a common interface providing the developers with easy integration of their custom parsers to the rest of the inference process.
It also provides a common configuration in the form of a properties panel in project properties for all depending modules.
And finally, this module holds common utility classes related to the task of processing data characteristic to the Schema documents. \\
Functionality is divided between separate packages, in the same order:

@@

Similar to the \code{Processor} implementations in the \code{BasicIGG} module, this is the core class of \code{XSDImporter} logic.
\code{XSDProcessor} registers itself into \emph{schema} input folder, \emph{xsd} file extension and declares it cannot handle other file extensions.\\
Class depends on NBP lookups (see \cite[section 4.1]{archdoc}) to find available parsers, and uses the selected parser to perform the import operation on defined files.
Initial grammar generated by this processor is considered \emph{complex} and should be followed by expansion (see \cite[section 4]{basiciggdoc}).

@@

Package \code{cz.cuni.mff.ksi.jinfer.xsdimporter.utils} contains classes available for all parsing methods.

@@

\begin{itemize}
	\item \code{getParser()} returns selected instance of \code{XSDParser}.
	\item \code{logLevel()} returns current log priority, messages with lower priority are not displayed.
	\item \code{isVerbose()} returns \code{true} or \code{false}, depending on the checkbox.
	\item \code{stopOnError()} returns \code{true} or \code{false}, depending on the checkbox.
\end{itemize}

@@

Enumeration of tag attributes currently recognized by our parsers. They are the following:
\begin{itemize}
	\item \code{name}
	\item \code{ref}
	\item \code{type}
	\item \code{use}
	\item \code{minOccurs}
	\item \code{maxOccurs}
\end{itemize}
List should be extended according to the parser, to reflect its functionality.

@@

Enumeration of tags currently known by our parsers. They are the following:
\begin{itemize}
	\item \code{schema}
	\item \code{element}
	\item \code{complexType}
	\item \code{sequence}
	\item \code{choice}
	\item \code{all}
	\item \code{attribute}
	\item \code{redefine} - this tag is not yet supported, but allows parsing of a certain types of documents
\end{itemize}
This list should also be updated in case the parser functionality is extended.

@@

@@

\subsubsection{DOM Helper}
Helper class for \code{DOMHandler}, containing ulility functions specific for DOM parsing method.
Two most notable of them are \code{createSentinel} and \code{finalizeElement}.

\begin{description}
	\item[CreateSentinel] Creates an instance of \code{Element} class, which is always a leaf in the rule-tree. This is useful when there are cyclic definitions in an input Schema document, or an \code{Element} with this name was defined previously and it is unnecessary to build a rule subtree for it again (it is a reference in this case). More information about sentinels can be found in \cite[section 3.2]{archdoc}, or \cite[section 4]{twostepdoc}.
	\item[FinalizeElement] Checks if \code{Element} is properly defined. Redefine it to \code{LAMBDA} when it was empty, or to token if it only contained a simple data type. This method allows for built-in data types of tags to be retained for export.
\end{description}

@@

\section{Data Flow}
Parsing of XSD begins when \code{IGGeneratorImpl} calls \code{XSDProcessor} with an input file.
The overall data flow while parsing a Schema document is simple, it can be summarized into following steps.
\begin{enumerate}
	\item \code{XSDProcessor} finds out the selected \code{XSDParser} from available service providers. This also indicates which module will be handling the actual parsing.
	\item \code{XSDProcessor} passes the input document to a selected module by calling \code{parse()} method on the selected \code{XSDParser}.
	\item Depending on the module, the corresponding API is used to extract IG rules from the input document.
	\item List of rules that were extracted from the document are returned to \code{XSDProcessor}.
	\item If no errors occured during this process, list of extracted rules is returned to \code{IGGeneratorImpl} for expansion. Otherwise, depending on the \emph{Print verbose info} setting, the inference is stops, or an empty list of rules for this input document is returned.
\end{enumerate}

@@

\begin{verbatim}
<xsd:complexType name="folderType">
  <xsd:sequence>
    <xsd:element name="file" type="fileType" />
  </xsd:sequence>
</xsd:complexType>

@@

<xsd:element name="folder" type="folderType" />
\end{verbatim}

@@

The modular design of the parser implementations is also an example of extensibility which can be achieved using the NetBeans platform. It allows developers to add, or remove, custom parsers just by creating a module with a new parser implementation; there is no need to change any code within \code{XSDImporter} module. Only exception is the re-definition of the default parser (currently DOM), which is not needed even if the module of default parser is not present.

Parsers with extended or custom functionality, can be created using \code{XSDImportDOM} module as example (recomended).

>>>>

None of the modules provide nor require any tokens. Complete dependency tree is described in \cite[section 4]{archdoc} and depicted in Figure 9 of that document.

@@

Firstly, it is an extension of the \code{BasicIGG} module, registering a service provider
of a \code{Processor} class, to handle files with \emph{xsd} extension (see \cite[section 3]{basiciggdoc}). 
It defines a common interface providing the developers with easy integration of their custom parsers to the rest of the inference process.
It also provides a common configuration in the form of a properties panel in project properties for all depending modules.
And finally, this module holds common utility classes related to the task of processing data characteristic to the Schema documents. \\
Functionality is divided between separate packages, in the same order as above:

@@

Similar to the \code{Processor} implementations in the \code{BasicIGG} module, this is the core class of \code{XSDImporter} logic.
\code{XSDProcessor} registers itself into \emph{schema} input folder, \emph{xsd} file extension and declares it cannot handle other file extensions.\\
Class depends on NBP lookups (see \cite[section 4.1]{archdoc}) to find available parsers, and uses the selected parser to perform the import operation on defined files.
Initial grammar generated by this processor is considered \emph{complex} and should be followed by expansion if necessary (see \cite[section 4]{basiciggdoc}).

@@

Package \code{cz.cuni.mff.ksi.jinfer.xsdimporter.utils} contains classes available to all parsing methods.

@@

\begin{itemize}
	\item \code{getParser()} returns selected instance of \code{XSDParser}.
	\item \code{logLevel()} returns current log priority, messages with lower priority are not displayed.
	\item \code{isVerbose()} returns \code{true} or \code{false}, depending on state of the checkbox.
	\item \code{stopOnError()} returns \code{true} or \code{false}, depending on state of the checkbox.
\end{itemize}

@@

Enumeration of tag attributes currently recognized by our parsers. They are the following.
\begin{itemize}
	\item \code{name}
	\item \code{ref}
	\item \code{type}
	\item \code{use}
	\item \code{minOccurs}
	\item \code{maxOccurs}
\end{itemize}
List should be extended according to the parser, to reflect its functionality.

@@

Enumeration of tags currently known by our parsers. They are the following.
\begin{itemize}
	\item \code{schema}
	\item \code{element}
	\item \code{complexType}
	\item \code{sequence}
	\item \code{choice}
	\item \code{all}
	\item \code{attribute}
	\item \code{redefine} - this tag is not yet supported, but allows parsing of a certain types of documents
\end{itemize}
This list should also be updated in case the parser functionality is extended.

@@

\paragraph{XSD Exception}

\code{XSDException} is a simple class extending \code{RuntimeException} to announce errors during import operation. It is catched by \code{XSDProcessor} which checks if \emph{Stop on error} setting is enabled and stops the inference.

@@

\subsubsection{DOM Helper}
Helper class for \code{DOMHandler}, containing ulility functions specific for DOM parsing method.
Two most notable of them are \code{createSentinel()} and \code{finalizeElement()}.

\begin{description}
	\item[CreateSentinel()] Creates an instance of \code{Element} class, which is always a leaf in the rule-tree. This is useful when there are cyclic definitions in an input Schema document, or an \code{Element} with this name was defined previously and it is unnecessary to build a rule subtree for it again (it is a reference in this case). More information about sentinels can be found in \cite[section 3.2]{archdoc}, or \cite[section 4]{twostepdoc}.
	\item[FinalizeElement()] Checks if \code{Element} is properly defined. Redefine it to \code{LAMBDA} when it was empty, or to token if it only contained a simple data type. This method allows for built-in data types of tags to be retained for export.
\end{description}

@@

\section{Data Flow}
Parsing of XSD begins when \code{IGGeneratorImpl} calls \code{XSDProcessor} with an input file.
The overall data flow while parsing a Schema document is simple, it can be summarized into following steps.
\begin{enumerate}
	\item \code{XSDProcessor} finds out the selected \code{XSDParser} from available service providers. This also indicates which module will be handling the actual parsing.
	\item \code{XSDProcessor} passes the input document to a selected module by calling \code{parse()} method on the selected \code{XSDParser}.
	\item Depending on the module, the corresponding API is used to extract IG rules from the input document.
	\item List of rules that were extracted from the document are returned to \code{XSDProcessor}.
	\item If no errors occured during this process, list of extracted rules is returned to \code{IGGeneratorImpl} for expansion. Otherwise, depending on the \emph{Stop on error} setting, the inference is stopped, or an empty list of rules for this input document is returned.
\end{enumerate}

@@

\begin{verbatim}
<xsd:complexType name="folderType">
  <xsd:sequence>
    <xsd:element name="file" type="fileType"/>
  </xsd:sequence>
</xsd:complexType>

@@

<xsd:element name="folder" type="folderType"/>
\end{verbatim}

@@

The modular design of the parser implementations is also an example of extensibility which can be achieved using the NetBeans platform. It allows developers to add, or remove, custom parsers just by creating a module with a new parser implementation; there is no need to change any code within \code{XSDImporter} module. Only exception is the re-definition of the default parser (currently DOM), which is not needed even if the module of default parser is not present.\\
Parsers with extended or custom functionality can be created using \code{XSDImportDOM} module as example (recomended).
